Object Categorization based on RGBD data

### 2014-01-06 Disseration/architecture.tex
done editing, now have to run some tests

\section{Software Functionality and Architecture}
	The programme resulting from this work is called ``Tagger3D'', for it's purpose is to tag an RGBD image of an object with a category label. The Bag of Words classification pipeline consists of four main parts discussed previously. In order to determine the best combination of algorithms for any given task an extensive research and evaluation has to be performed. In order to simplify the process the software system should be configurable, extensible and easy to maintain. Moreover, if it is to be used in any realistic setting it has to be efficient as well.

	\subsection{Required functionality}	
	There are three major functions that have to be supplied by the programme: (1) estimation, (2) batch inference and (3) inference. The first one is responsible for the model training. In order to perform this operation the following steps have to be completed: (i) detection and description of keypoints on the training set, (ii) codebook generation, (ii) classifier model training. The functions (2) and (3) are somewhat similar. Both require: (i) detection and description of keypoints on the test set, (ii) parsing keypoints' description into a visual vocabulary description and (iii) classification. The only is in the (i) step, e.g. the batch inference requires every image from the test set to be processed, whereas the inference can be done on any single image. The (3) have to be distinguished because it is the function that is to be used in a fully functional system mounted on i.e. a mobile robot.

		\subsubsection{Input/Output operations}	
		Additional functionality have to be provided in the field of input/output operations. Before any processing can be done each image have to be read into memory. Both batch inference and estimation are dataset dependant. What I mean by this is that a previously compiled database have to be accessible. The inference, on the other hand, is meant to be used in a production environment i.e. with a Kinect connected only. While the OpenNI Grabber framework from the PointCloud Library is essentially what is required for the inference, a little more elaboration has to be done on the demands of the estimation and batch inference environments. The two third party datasets used in the project have different formats and need to be tackled separately. The B3DO object dataset contains multiple objects in a single image. The locations of the images are available in xml files, while rgb and depth data are stored in separate files, 8-bit 3 channel jpeg and 16 bit one channel png respectively. Single objects have to be extracted from both pictures using the provided annotations and point cloud have to be build. The Zhang's dataset contain single objects. The rgb data is stored in 8 bit 3 channel jpegs and csv files contains euclidean coordinates of every rgb pixel. Both databases contain objects' labels that have to be loaded separately.

		A different problem is serialisation. If the models from the training stage are to be used during inference, they have to be serialised. This means that a standardised way of saving and loading of kMeans and SVM models have to be provided.

		\subsubsection{Configuration}		
		Every algorithm employed in the project have several configuration parameters. If the parameters were to be compiled with the code, every change would require a rebuild of the application or its parts. In order to address this issue a means of configuration from outside the code should be provided.

		\subsubsection{Interchangeability of algorithms}		
		Multitude of available algorithms makes it time consuming and computationally expensive to evaluate every available option. It should be possible to compile the programme with many algorithms suitable for performing the same task and decide which one should be used at run-time.

@@

	\begin{figure}[ht]
	\centering
	\includegraphics[width=1.0\textwidth]{figs/short}
	\caption{Tagger3D class diagram}
	\label{fig:class_diagram}
	\end{figure}

	The described functionality can be achieved in the following way. The utilisation of Object Oriented Programming (OOP) can lead to production of modular, flexible and extensible software. Using C++ as the language of choice can result in high efficiency. The excellent meta-programming tools provided by the C++ language help minimise the length of resulting hand-written code.

	\subsubsection{Configurability}
	In order to achieve configurability all the configuration parameters are stored in a configuration file. A separate object has been constructed for configuration file parsing. Simply called `Config', it makes use of the Boost.program\_options library to parse both the configuration file and command line arguments. It returns an associative array of (parameter, value) pairs. The convention is that if an object has to be configured the configuration map has to be passed in the object's constructor (other constructors are private).

@@

	\begin{figure}[ht]
	\centering
	\includegraphics[width=1.0\textwidth]{figs/short}
	\caption{Strategy pattern}
	\label{fig:strategy}
	\end{figure}

	Design patterns has been introduced for the very first time by Gamma \emph{et al} in \cite{gamma1993design}. They are best practices that should be used to solved common, recurring problems in software design. One of the patterns is the strategy pattern. It enables implementation of multiple algorithms handling some task and selection the desired behaviour at run-time. It is the exact problem encountered here. It is stated that an interface should be defined for each task and multiple classes encapsulating different algorithms for handling the tasks should realise those interfaces. One modification has been done: Algorithms have often some common operations, thus an idea of an interface (a class without any implemented methods) was dropped in favour of a virtual class.

	The strategy pattern was used for every processing step of the pipeline so as to make it extensible. One might want to enhance this solution by using an abstract factory design pattern, which has not been done in this case. It might make the code easier to maintain and read. However, the project is relatively small and the bulk of an abstract factory is unnecessary.

	There six five classes that can be treated as algorithms' interfaces in a strategy pattern. They are: ImgReader, PointNormal, Detector, Descriptor, Cluster, Predictor. Each of them contains pure virtual computation methods --- 'read` in case of the ImgReader or 'predict' in case of the Predictor. Additionally, they have some common methods defined --- I/O methods in Cluster or batch processing methods (such that take a vector of elements instead of a single element as input) for the Detector and the Descriptor. Every pure virtual class has its specialisations. For example there is the PFHDescriptor class with a Point Feature Histogram descriptor or a KMeansCluster employing kMeans clustering algorithm. The Tagger3D class chooses specialisations of the algorithms at run-time, depending on the configuration parameters.

>>>>

\section{Software Functionality and Architecture}

	We have decided to call our project ``Tagger3D''.  Since the purpose is to classify (or tag) point clouds, the name seems suitable. An optimal combination of algorithms for a bag of words pipeline is task and data specific. To find a combo of routines that yields superior performance we have to evaluate numerous algorithms. The process can be simplified; We are going to design an application that can be easily configured and extended. It should be possible to configure and choose an algorithm at run-time. Moreover, it should enable real time classification if it is to be used in any real setting.

	\subsection{Required functionality}	
	There are three major functions that have to be supported by the programme:
	\begin{enumerate}
	 \item train --- performs training
	 \item test --- evaluates the previously trained classifier
	 \item infer --- predicts a category of a single object
	\end{enumerate}

	Before any of them can be implemented, we have to identify common features. Inference and testing is very similar. The only difference is that the latter should process a whole testing dataset and compute statistics. The inference and training processes looks as follows:

	\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
		Inference:
		\begin{enumerate}
			\item RGBD image reading and preprocessing
			\item Point cloud construction
			\item Salient region identification
			\item Feature Extraction
			\item Vector Quantization
			\item Classification
		\end{enumerate} 
		&
		Training:
		\begin{enumerate}
		\item RGBD image reading and preprocessing
		\item Point cloud construction
		\item Salient region identification
		\item Feature Extraction
		\item Codebook Construction
		\item Vector Quantization
		\item Classificator training
		\end{enumerate} \\
	\end{tabular}

	The only differences is that training stage requires codebook construction and classifier training, whereas inference uses the classifier for prediction. If we compare training to testing it is clear that they both deal with large amounts of data. Inference is not that data-intensive and can be carried out for a single image. In order to simplify training we have decided to split the training and testing phases into several sub-routines. Such treatment let us change settings of an algorithm without the need to retrain the stages that lay before considered algorithm in the pipeline (\emph{e.g.} there is no need to extract features once more only because we have changed the dictionary size). The final application has the following operational modes, accessible from the command line:

	\begin{enumerate}
		\item Feature Extraction
		\item Codebook Generation
		\item Classifier Training
		\item Classifier Evaluation
		\item Inference
	\end{enumerate}

	In order to ensure that the application is configurable and easily extensible we used singleton and strategy design patterns and resorted to the Boost's program\_options package for configuration file parsing.

		\subsubsection{Input/Output operations}	
		This work is extremely data dependent. Every operation requires external data. Both training and testing a classifier consumes hundreds of images. Datasets used in this projects have different and incompatible formats. Not only an object responsible for run-time input/output operations is needed, but also a set of scripts for data preprocessing. Additionally, some serialisation method have to be supplied. The training of the classifier is far too computationally expensive to be computed every time the application starts. Once the classifier is trained, all the models should be stored for further usage. A way of saving and loading codebook and svm model is required.

		\subsubsection{Configuration}		
		Every algorithm used in this work have several configuration parameters. If the parameters were to be compiled with the code, every change would require a rebuild of parts of the application. A run-time configuration functionality is essential.

		\subsubsection{Interchangeability of algorithms}		
		Multitude of available algorithms makes it time consuming and computationally expensive to evaluate every available option. It should be possible to build the programme with a number of algorithms suitable for performing the same task and decide which one should be used at run-time.

@@

	\begin{figure}[ht]
	\centering
	\includegraphics[width=1.0\textwidth]{figs/class}
	\caption{Tagger3D class diagram}
	\label{fig:class_diagram}
	\end{figure}

	C++ is one of the most efficient languages on the market. It is perfect for Object Oriented Programming (OOP) --- a paradigm that makes writing modular, flexible and extensible software easier. The excellent meta-programming tools provided by the language help to minimise the length of the hand-written code. Among OOP's best practices is to use design patterns - a set of well-known, documented and tested methods of solving certain architectural problems. Using design patterns leads to cleaner code which is easier to maintain and reuse.

	\subsubsection{Configurability}
	The programme is configurable through a text file of a standard *.ini format. It should be formatted as follows:
	\begin{tabular}{c}
	 param1 = 2
	 param2 = aha
	 [section]
	 param3 = no
	\end{tabular}

	On top of the file there is a global section. Parameters can be accessed by their names. We can define sections but putting a section's name in brackets. the param3 can be accessed as ``section.param3''. An object ``Config'' was created for the purpose of configuration file parsing. It uses the Boost.program\_options module. Returned associative array of (parameter, value) pairs contains all parameters from a configuration file. We use a convention that if any object has to be configured by the configuration map it has to accept this map in it's constructor.

@@

	\begin{figure}[ht]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/strategy}
	\caption{Strategy pattern}
	\label{fig:strategy}
	\end{figure}

	Design patterns were for the very first time by Gamma \emph{et al} in 1993 \cite{gamma1993design}. They are best practices that should be used to solve recurring problems in software design. One of the patterns is the strategy pattern. It enables implementation of multiple algorithms to handle one task. Then, a specific algorithm can be selected at run-time. It is the exact problem encountered here. It is stated that an interface should be defined for each task and multiple classes encapsulating different algorithms for handling the task should realise the interface. One modification has been done: Algorithms have often some common operations, thus an idea of an interface (a class without any implemented methods) was dropped in favour of an abstract class with some methods implemented.

	The strategy pattern was used for every processing step of the pipeline so as to make it extensible. This property can be enhanced further by using a pattern of abstract factory. The idea was dropped in this case, however. The project is relatively small and the bulk of an abstract factory is beyond reason.

	Six parts of the pipeline are a subject of strategy pattern. The interfaces representing them are: ImgReader, PointNormal, Detector, Descriptor, Cluster, Predictor. Each of them contains pure virtual computation methods --- 'read` in case of the ImgReader or 'predict' in case of the Predictor. Additionally, they have some common methods defined --- I/O methods in Cluster or batch processing methods (such that take a vector of elements instead of a single element as an input) for the Detector and the Descriptor. Every pure virtual class have its specialisations. For instance there is the PFHDescriptor class with a Point Feature Histogram descriptor or a KMeansCluster employing kMeans clustering algorithm. The Factory class chooses specialisations of the algorithms at run-time, depending on the configuration parameters.

### 2014-01-06 Disseration/experiments.tex
done editing, now have to run some tests

\section{Experimental Setup}
	Thanks to the configurability of the programme the majority of experiments were run in a batch processing mode. That is a script in bash was written that allowed running multiple tests in series without any maintenance from the user. In a single series of tests any parameters could be modified or any data processing algorithm could be exchanged. All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz CPU, 8 GB of RAM and a nVidia M540 GPU.

\section{Experiments}
	The Bag of Words classification pipeline consists of four previously discussed steps. For there are many different algorithms suitable for each part of the pipeline, an extensive research is required in order to discover the best possible combination in a particular setting. The number of options grows combinatorial with number of candidates for each processing step. Moreover, many algorithms have different parameters that should be adjusted for any given conditions. Evaluation of every possibility is unfeasible due to the lack of time and computational power required. Even if only a single library, PCL, is considered, there are far too many options with 12 keypoint detectors and more than 20 feature description algorithms.

	\subsection{Detectors}
	In a paper \cite{pcl_keypoint_comparision} some keypoint detection algorithms from PCL are evaluated. It is stated that , albeit under slightly different conditions, the SIFT and ISS keypoint detectors achieve the highest performance. Therefore this paper compares only these two modules with respect to their usability in the BoW pipeline.

	\subsection{Descriptors}
	Recently a PCL's descriptors evaluation was performed in \cite{pcl_features}. The PFHRGB and SHOTCOLOR scored best. Only a little bit worse were PFH, FPFH, SHOT and USC. In this paper FPFH, PFH and PFHRGB are compared, motivation being that PFH is the original descriptor, FPFH is its approximate and thus faster version, while PFHRGB is an extension which makes use of colour information.

@@

	\subsection{Codebook}
	KMeans is used in almost every implementation of the Bag of Words image processing pipeline \cite{tsai2012bag, toldo2009bag}. Csurka \emph{et al} showed that the number of visual words or centroids have a significant impact on the final results \cite{csurka2004visual}. Therefore a number of tests were run in order to determine the optimal dictionary size.

>>>>

\section{Experimental Setup}
	Thanks to the configurability of the programme we were able to run the majority of experiments in a batch processing mode. That is, we wrote a script in bash that allowed running multiple tests in series without any maintenance. In a single series of tests any parameters could be modified or any data processing algorithm could be exchanged. All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz CPU, 8 GB of RAM and a nVidia M540 GPU.

\section{Experiments}	
	As already stated, a BoW pipeline consists of:
	\begin{inparaenum}[\upshape(1\upshape)]
	\item keypoint detection
	\item feature extraction 
	\item vector quantization and
	\item classification.
	\end{inparaenum}
	The number of possible combinations grows combinatorial with the amount of candidates for each part. We have to bear in mind that each algorithm contains a set of parameters that have to be adjusted for optimal performance. It would require a great deal of time and computational power to conduct exhaustive evaluation. Even if we consider only a single library --- PCL, we would have far too many options with 12 keypoint detectors and more than 20 feature descriptors. A literature review can help perform an early selection of algorithms.

	\subsection{Detectors}
	\rednote{run tests of SIFT, ISS, US}
	Keypoint detection algorithms have been compared with respect to repeatability, invariance \cite{pcl_keypoint_comparision} as well as object retrieval and recognition \cite{3d_keypoint_eval}. 3D-SIFT and ISS achieve the highest robustness for invariance. ISS appears to be the best choice for object retrieval. Dense detector (or uniform sampling) achieved the best performance in 2d image classification \cite{tsai2012bag}. Therefore, this paper compares SIFT, ISS and Uniform Sampling keypoint detection techniques.

	\subsection{Descriptors}
	\rednote{run tests on all PFH and SHOT descriptors and USC}
	PCL descriptors have been evaluated in terms of object retrieval performance \cite{pcl_features}. PFHRGB and SHOTCOLOR are the most successful. Simpler versions of those, that is: PFH, FPFH, SHOT and USC scored a little worse. We evaluate all of them in terms of BoW performance.

@@

	\subsection{Codebook}
	\rednote{implement and run fisher}
	KMeans is used in almost every implementation of the Bag of Words image processing pipeline \cite{tsai2012bag, toldo2009bag}. Csurka \emph{et al} showed that the number of visual words has a significant impact on the final results \cite{csurka2004visual}. We run a number of tests to determinate an optimal codebook size.

### 2014-01-06 Disseration/introduction.tex
done editing, now have to run some tests

	We use the following third party libraries in this work:
	\begin{itemize}
	 \item Boost\footnote{\url{http://www.boost.org/}} --- of the biggest general purpose libraries
	 \item OpenCV\footnote{\url{http://opencv.org/}} --- a general computer vision library
	 \item PointCloud Library\footnote{\url{http://pointclouds.org/}} \cite{PCL} --- a library for point cloud processing
	 \item libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} \cite{libsvm} --- a renown and very efficient SVM classifier implementation
	 \item Apache log4cxx\footnote{\url{http://logging.apache.org/log4cxx/}} --- Easy to use and intuitive logger
	\end{itemize}

	\subsection{PointCloud Library}
	Being nothing but a large scale open source project, it is a great processing tool for 2D images and 3D point clouds. Often abbreviated as PCL, it contains numerous state-of-the-art algorithms for feature detection, surface reconstruction, segmentation and many other subareas of computer vision. It is well documented and easy to use. Recently a machine learning library containing algorithms such as Support Vector Machine has been added. Some algorithms are multi-threaded thanks to the OpenMP library. A GPU module boosts some algorithms. Unfortunately the PCL is relatively new and its stability could be better. Currently available 1.7.0 version is going to be replaced by soon-to-be-announced 2.0 version with incompatible API.

	Every feature detector and descriptor used in this project comes from the PCL.

	\subsection{OpenCV}
	Considerably more mature, the OpenCV library is yet another great image processing library. A multitude of methods implemented in both C (OpenCV 1.x) and C++ (OpenCV 2.x) allows for production of fully functional image processing or computer vision application with this single library. There are many machine learning mechanisms as well. Among them one can find kMeans, Gaussian Mixture Model, Na\`ive Bayes or a Support Vector Machine. Some of the more demanding in terms of computational power are parallelized with Threading Building Blocks (TBB). A module exploiting powers of the nVidia's CUDA technology exists in order to enhance computation even more.

	In this paper OpenCV is used for input/output operations, image preprocessing. KMeans and SVM implementations are used as well.

	\subsection{Boost}
	Boost is a general purpose library. It contains more than 50 separate libraries, 12 of which were incorporated into the new C++11 standard. One of the most popular are libraries for smart pointers, multi-threading or meta-programming. Tagger3D uses only the functionality provided by the Boost.program\_options library. It enables convenient parsing of configuration files and command line arguments.

@@

	Multiple RGBD datasets were created. The purpose of authors of the vast majority of them were to provide a benchmark for tasks of tracking or instance-level object recognition. Others have small number of categories or very few examples in every category. Unfortunately, the most are not fit for the object classification problem.
	The RGB-D object dataset from the University of Washington \cite{dataset_washington} would be perfect, if not for the fact that it consists of video sequences. A technology like Kinect Fusion \cite{KinectFusion} makes it relatively easy to build a detailed 3D model (a point cloud or a mesh) from such data. The only problem is in the computational cost of this method and actions required to gather such data --- in a real setting a mobile robot would have to circle an object. Two datasets are used are for the purpose of this paper. The first one is the Berkeley 3D Object dataset \cite{B3DO} and the second one is a dataset compiled by Zhang \emph{et al} at the University of Tokyo \cite{zhangcategory}. The datasets are going to be abbreviated as B3DO and Tokyo datasets respectively

@@

	The Berkeley 3D Object dataset was specifically designed for the purpose of object classification. It consists of cluttered images in indoor environment. There are around 50 classes with more than 20 examples in each of them. RGBD data is provided as pairs of images. There are 8 bit RGB jpeg pictures and 16 bit png files containing depth data in millimetres. Images are densely labelled --- for every pair of images there is an xml with annotations. Every annotation is comprised of a category label, bounding box coordinates and object's orientation.

	Before the B3DO database could be used it had to be preprocessed. Neither image segmentation nor object detection are addressed in this paper. Because of that the objects had to be extracted from the cluttered images.

@@

	The dataset compiled at the University of Tokyo is comprised of high quality images of objects in different settings. Factors such as viewpoint, object orientation, object's texture and environments are changing on different images. The aim of the authors of this dataset was slightly different - it was object detection and classification in casual images. There are 10 classes with varying amounts of per class examples. The database is available as two sets of files: 8 bit RGB jpeg files and csv files containing euclidean coordinates of every pixel in the corresponding colour image.

>>>>

	We use the following third party C++ libraries:
	\begin{itemize}
	 \item Boost\footnote{\url{http://www.boost.org/}} --- of the biggest general purpose libraries
	 \item OpenCV\footnote{\url{http://opencv.org/}} --- a general computer vision library
	 \item PointCloud Library\footnote{\url{http://pointclouds.org/}} \cite{PCL} --- a library for point cloud processing
	 \item libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} \cite{libsvm} --- a renown and very efficient SVM classifier implementation
	 \item Apache log4cxx\footnote{\url{http://logging.apache.org/log4cxx/}} --- Easy to use and intuitive logger
	\end{itemize}

	\subsection{Boost}
	Boost is a general purpose library available under the Boost Software License\footnote{\url{http://www.boost.org/LICENSE_1_0.txt}}. It is free for both commercial and non-commercial use. Boost comprises of more than 50 separate libraries. 12 of the most popular libraries have been incorporated into the new C++11 standard. Because of that, Boost may become redundant in many applications. The original library had contained conveniences such as smart pointers, multi-threading utilities and meta-programming tools. We excessively use smart pointers and meta-programming utilities; but the only package from the trimmed down Boost used in this project is the Boost.program\_options library. It enables convenient parsing of configuration files and command line arguments.

	\subsection{OpenCV}
	OpenCV is a general computer vision library available under the BSD License\footnote{\url{http://opensource.org/licenses/BSD-3-Clause}}. It is free for commercial and non-commercial use. It was designed for computational efficiency and real-time applications. OpenCV takes advantage of the underlying hardware employs hardware-specific optimisation e.g. SSE4. Some algorithms are written in nVidia CUDA and can use GPU for faster execution. Others use Threading Building Blocks (TBB, Intel's multithreading library) to enable concurrency. OpenCV is available for the most popular desktop and mobile platforms. It is written in optimised C and C++ and provides two interfaces: the original OpenCV 1.x C interface and a newer OpenCV 2.x C++ interface. This single library allows production of fully functional computer vision programmes. Many machine learning routines are available, too. Among them are: kMeans, Gaussian Mixture Model, Na\`ive Bayes, SVM, Random Forests and Boosting. We use OpenCV for input/output operations, image processing and vector quantization.

	\subsection{PointCloud Library}
	PointCloud Library (PCL) is a computer vision library suitable for point clouds processing, manipulation and visualisation. It is released under the BSD license and is free for both commercial and non-commercial use. PCL contains numerous state-of-the-art algorithms for feature detection, surface reconstruction, segmentation to name just a few areas. It is well documented and easy to use. Recently, a machine learning module containing SVM, kMeans and other algorithms. Some routines are multi-threaded thanks to the OpenMP library. A GPU module makes use of CUDA to lessen computation time. Unfortunately, the PCL is relatively new and its stability could be better. Currently available 1.7.1 version is going to be replaced by a soon-to-be-announced 2.0 version with incompatible API. In this project we try to build an application for point cloud applications. We extensively use PCL for operations like downsampling, keypoint detection, feature extraction.

	\subsection{libsvm}
	\rednote{describe}
	\subsection{Apache log4cxx}
	\rednote{describe}

@@

	Machine Learning algorithms provide a way of learning a function that maps input to the desired output. Classification algorithms require supervised training and labelled data. If we wanted to compare any algorithms we would have to do so on a common dataset. That is why multiple scientific datasets have been created: ImageNet\footnote{\url{http://www.image-net.org/}}, PascalVoc\footnote{\url{http://pascallin.ecs.soton.ac.uk/challenges/VOC/}}, LabelMe\footnote{\url{http://labelme.csail.mit.edu/Release3.0/browserTools/php/dataset.php}} and SUN\footnote{\url{http://groups.csail.mit.edu/vision/SUN/}} among others. Unfortunately, they contain RGB and grayscale images without any depth information. Therefore they cannot be used in this paper. On the other hand, the vast majority of RGBD datasets are focused on tracking or instance-level recognition. Others have very few categories or insufficient number of examples per category. We managed to find only two datasets suited to our needs. They are: the Berkeley 3D Object (B3DO) dataset \cite{B3DO} and a dataset compiled by Zhang \emph{et al} at the University of Tokyo\cite{zhangcategory}. The latter will be abbreviated Tokyo dataset from now on.

	An interesting dataset is provided by the University of Washington \cite{dataset_washington}. It consists of video sequences that capture objects' round views in RGBD. Kinect Fusion\footnote{\url{http://msdn.microsoft.com/en-us/library/dn188670.aspx}} technology could be used to prepare excellent point clouds from the videos. We have decided against it, for a huge computational cost associated with this way of point cloud construction. Furthermore, in a real setting a mobile robot would have to circle an object in order to gather enough data.

@@

	The Berkeley 3D Object dataset was specifically designed for the purpose of object detection and classification. It consists of cluttered images in indoor environment. There are around 50 classes with more than 20 examples in each of them. RGBD data are provided as pairs of colour images (8 bit RGB jpeg files) and depth maps (16 bit png files). Images are densely labelled --- for every pair of images there is an xml file with annotations. Each annotation states a category of an object as well as it's bounding box location. Images are cluttered, with many labelled and random objects per image. Labelled objects are often partially occluded. We do not address image segmentation nor object detection; we had to extract objects from the images before we could use the dataset.

@@

	The Tokyo dataset is comprised of high quality images of objects in different settings, with changing viewpoint, object orientation and texture. The dataset is presented as colour images (8 bit RGB jpeg files) and depth maps (csv files with XYZ coordinates of each pixel).	This dataset is aimed at the task of object classification in casual images. There is one labelled object per image, without any bounding box given. Scenes are sometimes cluttered, with many random objects present at a scene.
